### 2014-10-22 PAPER_AMMLY.tex
Significant simplifications

Neural networks are machine learning models used for learning complex and highly non-linear mathematical functions in the context of regression, classification, pattern recognition, clustering, reinforcement learning etc. Modern neural networks historically originate from simple early models such as threshold logic~\cite{mcculloch43a}, Hebbian network~\cite{Hebb:1949} and perceptron~\cite{rosenblatt58a} that were followed by more sophisticated models including Hopfield network~\cite{Hopfield:1988:NNP:65669.104422}, Kohonen network~\cite{Kohonen1982}, and Boltzman machines~\cite{Hinton:1986:LRB:104279.104291} (and many others). Despite their modeling power, the interest in learning with early neural network significantly weakened when it was shown that they have several limitations including: i) learning limitations such as the inability of single-layer networks to solve the XOR problem~\cite{minsky69perceptrons}, ii) long training time of large networks and proness to overfitting~\cite{JMLR:v15:srivastava14a}, and iii) getting stuck in poor-quality local optima or saddle points while training~\cite{Larochelle:2009:EST:1577069.1577070}. Today many of these limitations can be solved with the development of new efficient training strategies (among them backpropagation algorithm~\cite{Werbos:74} which enables to solve the XOR problem), fast GPU-based implementations significantly reducing the training time, and techniques preventing the overfitting such as dropout (e.g.~\cite{JMLR:v15:srivastava14a}). Therefore, after a long period of scepticism, the paradigm of learning with neural networks gained significant attention in recent years resulting in many new architectures, such as convolutional networks~\cite{lecun-gradientbased-learning-applied-1998}, recurrent neural networks~\cite{Graves:2009:NCS:1525650.1525782}, deep feedforward neural networks (e.g.~\cite{DBLP:journals/corr/Schmidhuber14} or wide networks~\cite{Huang14}, where the most fundamental difference between them and their early predecessors lies in a much larger parameter space (throughout the paper we refer to the number of network parameters as network size). In effect, the optimization problem arising when training these models is highly non-convex with exponentially many critical points. Despite the apparent difficulty of this optimization, modern neural network approaches often beat state-of-the-art results on a plethora of learning tasks (pattern recognition~\cite{journals/nn/CiresanMMS12}, brain image segmentation~\cite{NIPS2012_4741}, human pose estimation~\cite{DBLP:journals/corr/TompsonJLB14}, large-scale visual recognition~\cite{sermanet-iclr-14}, transfer learning~\cite{conf/icml/GoodfellowCB12} and many more) which is highly suggestive of their ability to recover high-quality solution to the optimization problem. The fundamental question arises: 'Why?'

@@

For the theoretical analysis, we consider a simple model of the fully-connected feed-forward deep network with a single output and rectified linear units. We call the network $\mathcal{N}$. We focus on a binary classification task. Let $X$ be the random input vector of dimensionality $d$. Let $(H-1)$ denote the number of hidden layers in the network and we will refer to the input layer as the $0^{\text{th}}$ layer and to the output layer as the $H^{\text{th}}$ layer. Let $n_i$ denote the number of units in the $i^{\text{th}}$ layer (note that $n_0 = d$ and $n_H = 1$). Let $W_i$ be the matrix of weights between $(i - 1)^{\text{th}}$ and $i^{th}$ layers of the network. Also, let $\sigma$ denotes the activation function that converts a unit's weighted input to its output activation. We consider linear rectifiers thus $\sigma(x) = \max(0,x)$. We can therefore write that for any given random input vector $X$, the network gives the following (random) output $Y$:
\[Y = q\sigma(W_H^{\top}\sigma(W_{H-1}^{\top}\dots\sigma(W_1^{\top}X)))\dots),
\]
where $q = \sqrt{\frac{n_0n_1 + n_1n_2 + ... + n_{H-1}n_H}{n_0n_1...n_H}}$ is simply a normalization factor. The same expression for the output of the network can be re-expressed in the following way:
\begin{equation}
Y = q\sum_{i=1}^{n_0}\sum_{j = 1}^\gamma X_{i}A_{i,j}\prod_{k = 1}^{H}w_{i,j}^{(k)},
\label{eq:befrein}
\end{equation}
where the first summation is over the network inputs and the second one is over all paths from a given network input to its output, where $\gamma$ is the total number of such paths (note that $\gamma = n_1n_2\dots n_H$). Furthermore, $w_{i,j}^{(k)}$ is the weight of the $k^{\text{th}}$ segment of path indexed with $(i,j)$ which connects layer $(k-1)^{st}$ with layer $k^{\text{th}}$ of the network. Note that each path corresponds to a certain set of $H$ weights, which we refer to as a \textit{configuration of weights}, which are multiplied by each other. Random variable $A_{i,j}$ denotes whether path $(i,j)$ is active ($A_{i,j} = 1$) or not ($A_{i,j} = 0$). For our theoretical analysis we assume that $X$'s are identically distributed such that $X_{i_1,i_2,\dots,i_H}\sim\mathcal{N}(0,1)$.

\begin{definition}
The mass of the network $\Psi$ is the total number of all paths between all network inputs and outputs: $\Psi = \prod_{i=0}^Hn_i$.
\end{definition}

\begin{definition}
The size of the network $\Lambda$ is the total number of network parameters: $\Lambda = \sum_{i=0}^{H-1}n_in_{i+1}$.
\end{definition}

There mass and the size of the network depend on each other as captured in Theorem~\ref{thm:arge}.
\begin{theorem}
Let $\Psi$ be the mass of the network, $d$ be the number of network inputs and $H$ be the depth of the network. The size of the network is bounded as
\[\Psi^2\frac{1}{d} \geq \Lambda \geq \sqrt[H]{\Psi^2}\frac{H}{\sqrt[H]{d}} \geq \sqrt[H]{\Psi}.
\]
\label{thm:arge}
\end{theorem}

@@

In this section we introduce certain assumptions regarding the neural network model. These assumptions consider random variables $X$s and $A$s (their distributions and mutual dependencies) as well as they introduce spherical constraint on the model weights. We also introduce two other assumptions regarding redundancy of network parameters and their uniformity (details in the text below), both of them are justified by empirical evidence in the literature. The aim of this section is to obtain an approximator to the expectation $\mathbb{E}_A[Y]$ (note it is still a random variable) which, as will be seen in Section~\ref{subsec:LFSG}, is used in the definition of the loss function of neural network. Theorems~\ref{thm:redun} and~\ref{thm:unif} provide some guarantees regarding the quality of this approximation.

\paragraph{Equally likely paths}
We assume each path in Equation~\ref{eq:befrein} is equally likely to be active thus $A_{i,j}$'s will be modelled as Bernoulli random variables with the same probability of success $\rho$. By assuming the independence of $X$'s and $A's$ we get the following
\begin{equation}
\mathbb{E}_A[Y] = q\sum_{i=1}^{n_0}\sum_{j = 1}^\gamma X_{i}\rho\prod_{k = 1}^{H}w_{i,j}^{(k)}.
\label{eq:befrein2}
\end{equation}

\paragraph{Spherical constraint}
Let $\mathcal{W} = \{w_1,w_2,\dots,w_{\Lambda}\}$ be the set of all weights of the network. We make a benign assumption that the weights sattisfy the spherical condition 
\begin{equation}
\frac{1}{\Lambda}\sum_{i=1}^{\Lambda}w_i^2 = \mathcal{C},
\label{eq:befspherical}
\end{equation}
where $\mathcal{C}$ is some positive constant.

\paragraph{Redundancy in network parametrization}
Let $\mathcal{A}$ denote the set of all $H$-length configuration of weights chosen from $\mathcal{W}$ (order of weights in a configuration does matter). Note that the size of $\mathcal{A}$ is therefore $\Lambda^H$. Also let $\mathcal{B}$ be a set such that each element correspond to the single configuration of weights from Equation~\ref{eq:befrein2}, thus $\mathcal{B} = \{(w_{1,1}^1,w_{1,1}^2,\dots,w_{1,1}^H),(w_{1,2}^1,w_{1,2}^2,\dots,w_{1,2}^H),\dots,\\(w_{n_0,\gamma}^1,w_{n_0,\gamma}^2,\dots,w_{n_0,\gamma}^H)\}$, where every single weight comes from set $\mathcal{W}$. Note that in general there exist elements in $\mathcal{A}$ that will never appear in $\mathcal{B}$ (unless we allow repetition of weights in $\mathcal{W}$). Thus Equation~\ref{eq:befrein2} can be equivalently written as 
\begin{equation}
Y_{\Lambda} \!:=\! \mathbb{E}_A[Y] \!=\! q\!\!\!\!\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}\!\!\!\!\!\!\!\!\!\!\!r_{i_1\!,i_2,\dots,i_H}\!X_{i_1,i_2,\dots,i_H}\rho\!\prod_{k = 1}^{H}\!\!w_{i_k},
\label{eq:befapprox}
\end{equation}
where $r_{i_1,i_2,\dots,i_H}$ denotes whether the configuration $(w_{i_1},w_{i_2},\dots,w_{i_H})$ appeared in Equation~\ref{eq:befrein2} or not thus $r_{i_1,i_2,\dots,i_H} \in \{0\cup{1}\}$ and furthermore $\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}r_{i_1,i_2,\dots,i_H} = \Psi$. In the notation $Y_{\Lambda}$, index $\Lambda$ refers to the number of unique weights of a network (this notation will be helpful later in this section).

@@

\paragraph{Uniformity}
Consider $(s,\epsilon)$-reduction image of $\mathcal{N}$ for some $s \leq \Lambda$ and $\epsilon \in [0,1]$. The output $Y_s$ of the image network can in general be expressed as
\[Y_s = q\!\!\!\sum_{i_1,\dots,i_H=1}^{s}\!\!\!\sum_{j=1}^{r_{i_1,\dots,i_H}^{'}}X_{i_1,\dots,i_H}\rho\prod_{k = 1}^{H}\!\!w_{i_k},
\]
where $r_{i_1,\dots,i_H}^{'} \in \{\mathbb{Z}^{+}\cup{0}\}$ is the number of times each configuration $(w_{i_1},w_{i_2},\dots,w_{i_H})$ repeats in Equation~\ref{eq:befapprox} and $\sum_{i_1,\dots,i_H=1}^{s}r_{i_1,\dots,i_H}^{'} = \Psi$. We can further rewrite $Y_s$ as follows
\[Y_s = q\!\!\!\sum_{i_1,\dots,i_H=1}^{s}\!\!\underbrace{\left(\!\sum_{j=1}^{r_{i_1,\dots,i_H}^{'}}\!\!\!X_{i_1,\dots,i_H} + 0 + \dots + 0\right)}_{r_{i_1,\dots,i_H}^{''} \text{summands}}\!\!\rho\prod_{k = 1}^{H}\!\!w_{i_k},
\]
where $r_{i_1,\dots,i_H}^{''} \in \{\mathbb{Z}^{+}\cup{0}\}$ is the number of times each configuration $(w_{i_1},w_{i_2},\dots,w_{i_H})$ would repeat in Equation~\ref{eq:befapprox} if all $r_{i_1,\dots,i_H}$ would be equal to $1$ and $\mathcal{W}$ would have $s$ unique weights and the remaining $(\Lambda - s)$ weights were repetitions\footnote{Note that each $r_{i_1,\dots,i_H}^{''}$ is not uniquely defined here as one could consider many different ways of constructing $\mathcal{W}$ by repeating the same weights different times.}. We therefore require that $r_{i_1,\dots,i_H}^{''} \in \{\mathbb{Z}^{+}\cup{0}\}$, $r_{i_1,\dots,i_H}^{''} \geq r_{i_1,\dots,i_H}^{'}$ and $\sum_{i_1,\dots,i_H=1}^{s}r_{i_1,\dots,i_H}^{''} = \Lambda^H$. \textcolor{red}{We should provide the decoupling inequality as exact equality does not hold!} We furthermore define $Z$'s to be independend standard normal random variables satisfying the following equation (plethora of similar decoupling strategies are discussed in~\cite{opac-b1095246})
\[\sum_{j=1}^{r_{i_1,\dots,i_H}^{'}}X_{i_1,\dots,i_H} = \sum_{j=1}^{r_{i_1,\dots,i_H}^{''}} \sqrt{\frac{r_{i_1,\dots,i_H}^{'}}{r_{i_1,\dots,i_H}^{''}}}Z_{i_1,\dots,i_H}^{(j)}. 
\]
Let $\hat{r}_{i_1,\dots,i_H}^{(j)} = \sqrt{\frac{r_{i_1,\dots,i_H}^{'}}{r_{i_1,\dots,i_H}^{''}}}$. Therefore
\begin{eqnarray*}
Y_s &=& q\sum_{i_1,\dots,i_H=1}^{s}\sum_{j=1}^{r_{i_1,\dots,i_H}^{''}}\hat{r}_{i_1,\dots,i_H}^{(j)}Z_{i_1,\dots,i_H}^{(j)}\rho\prod_{k = 1}^{H}w_{i_k}\\
&=& \sum_{i_1,\dots,i_H=1}^{\Lambda}\hat{r}_{i_1,\dots,i_H}Z_{i_1,\dots,i_H}\rho\prod_{k = 1}^{H}w_{i_k},
\end{eqnarray*}
where the last step comes from re-indexing terms.

Finally we assume that unique weights are close to being evenly distributed on the graph of connections of network $\mathcal{M}$. We call this assumption a \textit{uniformity assumption} (note it is analogous to the maximum entropy assumption). This assumption is in general consistent with the approach in~\cite{NIPS2013_5025}. To be more specific, this assumption implies that for all $(i_1,i_2,\dots,i_H):i_1,i_2,\dots,i_H \in \{1,2,\dots,H\}$ there exists non-negative constant $c$ and $\delta \in [0,1]$ such that the following holds
\begin{equation}
c\delta\sqrt{\frac{\Psi}{\Lambda^H}} \leq \hat{r}_{i_1,i_2,\dots,i_H} \leq c\sqrt{\frac{\Psi}{\Lambda^H}},
\label{eq:uniform}
\end{equation}
where the factor $\sqrt{\frac{\Psi}{\Lambda^H}}$ comes from the fact that for the network where every weight is uniformly distributed on the graph of connections (thus every node has equal probability of being adjacent to an edge with any of the unique weights) it holds that $\hat{r}_{i_1,i_2,\dots,i_H} = \sqrt{\frac{\Psi}{\Lambda^H}}$. Note that this condition can be sattified with large $\delta$ (close to $0$) if $s$ is sufficiently small.

Consider therefore an expression as follows
\begin{equation}
\hat{Y}_s = q\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}\sqrt{\frac{\Psi}{\Lambda^H}}Z_{i_1,i_2,\dots,i_H}\rho\prod_{k = 1}^{H}w_{i_k},
\label{eq:approx}
\end{equation}
which can be thought of as an output of some network $\mathcal{M}$ where the weights are still chosen from $\mathcal{A}$ but there are only $s$ unique weights in $\mathcal{A}$ among the total of $\Lambda$ weights, and furthermore every $H$ - length configuration of weights chosen from $\mathcal{A}$ is equally likely. Then the following theorem (Theorem~\ref{thm:unif}) captures the connection between $\hat{Y}_s$ and $Y_{\Lambda}$.

\begin{theorem}
Under the uniformity assumption of Equation~\ref{eq:uniform}, random variable $\hat{Y}_s$ in Equation~\ref{eq:approx} and random variable $Y_{\Lambda}$ in Equation~\ref{eq:befapprox} sattisy the following
\[corr(\hat{Y}_s,Y_{\Lambda}) \geq \delta
\]
\label{thm:unif}
\end{theorem}

We will refer to $\hat{Y}_s$ as an $(s,\epsilon,\delta)$-\textit{approximator} of $Y_{\Lambda}$, where the quality of this approximation is captured in Theorems~\ref{thm:redun} and~\ref{thm:unif}. Intuitively, for large-size networks (our analysis in Section~\ref{sec:theory} considers $\Lambda \rightarrow \infty$) one would expect $s$ to be small enough to simultaneously guarantee sufficiently large (close to $1$) $\delta$ and preserve good accuracy (small $\epsilon$). \textcolor{red}{That is because large networks have significantly more modelling power thus small $s$ is a natural form of controlling the overfitting. Besides then the data is mapped to a higher dimensional space.} In the next we will consider two frequently used loss functions, absolute loss and hinge loss, where we approximate $Y_{\Lambda}$ with $\hat{Y}_s$.

@@

where $Y_t$ is a random variable corresponding the true data labeling that takes values $-S$ or $S$ in case of the absolute loss and $-\frac{1}{S}$ or $\frac{1}{S}$ in case of the hinge loss, where $S = \sup_{\bf{w}}{\hat{Y}_s}$. Also note that in case of the hinge loss $\max$ operator can be modelled as Bernoulli random variable, that we will refer to as $M$, with success ($M = 1$) probability $\rho^{'} = \frac{1}{\rho\sqrt{\mathcal{C}^H}}$. We assume $M$ is independent of $\hat{Y}_s$. Therefore we obtain that

@@

  $\!\!\!\!\!\!\mathbb{E}_{M}[M(1 - \frac{1}{S}\hat{Y}_s)]$ $\:\:\:\:$if$\:\:\:\:$ $Y_t = \frac{1}{S}$ \\
  $\!\mathbb{E}_{M}[M(1 + \frac{1}{S}\hat{Y}_s)]$ $\:\:\:\:$if$\:\:\:\:$ $Y_t = -\frac{1}{S}$ \\

@@

  $\!\mathbb{E}_{M}[M(s_1 - s_2\hat{Y}_s)]$ $\:\:\:\:$if$\:\:\:\:$ $Y_t  > 0$ \\
  $\!\mathbb{E}_{M}[M(s_1 + s_2\hat{Y}_s)]$ $\:\:\:\:$if$\:\:\:\:$ $Y_t < 0$ \\

@@

where in case of absolute loss $\rho^{'} = 1$, $s_1 = S$ and $s_2 = 1$, whereas for hinge loss $s_1 = 1$ and $s_2 = \frac{1}{S}$. Furthermore, since $X$'s are Gaussian random variables, then so are $-X$'s thus we can further generalize that

@@

\mathcal{L}_{\Lambda,H}({\bm w}) \!\!\!\!\!&=&\!\!\!\!\! \mathbb{E}_{M}[M(s_1 + s_2\hat{Y}_s)]\\
&=& \!\!\!\!\!s_1\rho^{'} \!+\! s_2\rho^{'}\hat{Y}_s\\
&=& \!\!\!\!\!s_1\rho^{'} \!+\! s_2q\sqrt{\!\!\frac{\Psi}{\Lambda^H}\!\!\!\!}\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}\!\!\!\!\!\!\!Z_{i_1,i_2,\dots,i_H}\rho\rho^{'}\prod_{k = 1}^{H}w_{i_k}.

>>>>

Neural networks are machine learning models used for learning complex and highly non-linear mathematical functions in the context of regression, classification, pattern recognition, clustering, reinforcement learning etc. Modern neural networks historically originate from simple early models such as threshold logic~\cite{mcculloch43a}, Hebbian network~\cite{Hebb:1949} and perceptron~\cite{rosenblatt58a} that were followed by more sophisticated models including Hopfield network~\cite{Hopfield:1988:NNP:65669.104422}, Kohonen network~\cite{Kohonen1982}, and Boltzman machines~\cite{Hinton:1986:LRB:104279.104291} (and many others). Despite their modeling power, the interest in learning with early neural network significantly weakened when it was shown that they have several limitations including: i) learning limitations such as the inability of single-layer networks to solve the XOR problem~\cite{minsky69perceptrons}, ii) long training time of large networks and proness to overfitting~\cite{JMLR:v15:srivastava14a}, and iii) getting stuck in poor-quality local optima or saddle points while training~\cite{Larochelle:2009:EST:1577069.1577070}. Today many of these limitations can be solved with the development of new efficient training strategies (among them backpropagation algorithm~\cite{Werbos:74} which enables to solve the XOR problem), fast GPU-based implementations significantly reducing the training time, and techniques preventing the overfitting such as dropout (e.g.~\cite{journals/corr/abs-1207-0580,JMLR:v15:srivastava14a}). Therefore, after a long period of scepticism, the paradigm of learning with neural networks gained significant attention in recent years resulting in many new architectures, such as convolutional networks~\cite{lecun-gradientbased-learning-applied-1998}, recurrent neural networks~\cite{Graves:2009:NCS:1525650.1525782}, deep feedforward neural networks (e.g.~\cite{DBLP:journals/corr/Schmidhuber14} or wide networks~\cite{Huang14}, where the most fundamental difference between them and their early predecessors lies in a much larger parameter space (throughout the paper we refer to the number of network parameters as network size). In effect, the optimization problem arising when training these models is highly non-convex with exponentially many critical points. Despite the apparent difficulty of this optimization, modern neural network approaches often beat state-of-the-art results on a plethora of learning tasks (pattern recognition~\cite{journals/nn/CiresanMMS12}, brain image segmentation~\cite{NIPS2012_4741}, human pose estimation~\cite{DBLP:journals/corr/TompsonJLB14}, large-scale visual recognition~\cite{sermanet-iclr-14}, transfer learning~\cite{conf/icml/GoodfellowCB12} and many more) which is highly suggestive of their ability to recover high-quality solution to the optimization problem. The fundamental question arises: 'Why?'

@@

For the theoretical analysis, we consider a simple model of the fully-connected feed-forward deep network with a single output and rectified linear units. We call the network $\mathcal{N}$. We focus on a binary classification task. Let $X$ be the random input vector of dimensionality $d$. Let $(H-1)$ denote the number of hidden layers in the network and we will refer to the input layer as the $0^{\text{th}}$ layer and to the output layer as the $H^{\text{th}}$ layer. Let $n_i$ denote the number of units in the $i^{\text{th}}$ layer (note that $n_0 = d$ and $n_H = 1$). Let $W_i$ be the matrix of weights between $(i - 1)^{\text{th}}$ and $i^{th}$ layers of the network. Also, let $\sigma$ denotes the activation function that converts a unit's weighted input to its output activation. We consider linear rectifiers thus $\sigma(x) = \max(0,x)$. We can therefore write that for any given random input vector $X$, the network gives the following (random) output $Y$:
\[Y = q\sigma(W_H^{\top}\sigma(W_{H-1}^{\top}\dots\sigma(W_1^{\top}X)))\dots),
\]
where $q = \sqrt{(n_0n_1...n_H)^{(H-1)/2H}}$ is simply a normalization factor. The same expression for the output of the network can be re-expressed in the following way:
\begin{equation}
Y = q\sum_{i=1}^{n_0}\sum_{j = 1}^\gamma X_{i}A_{i,j}\prod_{k = 1}^{H}w_{i,j}^{(k)},
\label{eq:befrein}
\end{equation}
where the first summation is over the network inputs and the second one is over all paths from a given network input to its output, where $\gamma$ is the total number of such paths (note that $\gamma = n_1n_2\dots n_H$). Furthermore, $w_{i,j}^{(k)}$ is the weight of the $k^{\text{th}}$ segment of path indexed with $(i,j)$ which connects layer $(k-1)^{st}$ with layer $k^{\text{th}}$ of the network. Note that each path corresponds to a certain set of $H$ weights, which we refer to as a \textit{configuration of weights}, which are multiplied by each other. Finally, $A_{i,j}$ denotes whether a path $(i,j)$ is active ($A_{i,j} = 1$) or not ($A_{i,j} = 0$).

\begin{definition}
The mass of the network $\Psi$ is the total number of all paths between all network inputs and outputs: $\Psi = \prod_{i=0}^Hn_i$. We will also denote $\Lambda$ to be $\Lambda = \sqrt[H]{\Psi}$.
\end{definition}

\begin{definition}
The size of the network $N$ is the total number of network parameters: $N = \sum_{i=0}^{H-1}n_in_{i+1}$.
\end{definition}

There mass and the size of the network depend on each other as captured in Theorem~\ref{thm:arge}.
\begin{theorem}
Let $\Psi$ be the mass of the network, $d$ be the number of network inputs and $H$ be the depth of the network. The size of the network is bounded as
\[\Psi^2\frac{1}{d} \geq N \geq \sqrt[H]{\Psi^2}\frac{H}{\sqrt[H]{d}} \geq \sqrt[H]{\Psi} = \Lambda.
\]
\label{thm:arge}
\end{theorem}
\begin{corollary}
For bounded network depth $H$, $\Lambda \rightarrow \infty$ iff $\Psi \rightarrow \infty$. For bounded network depth $H$, if the mass of the network $\Psi$ goes to $\infty$ ($\Psi \rightarrow \infty$) then the size of the network also goes to $\infty$ ($N \rightarrow \infty$) (equivalently $\Lambda \rightarrow \infty$ implies $N \rightarrow \infty$). 
\end{corollary}

@@

In this section we introduce randomness to the model and assume $X$s and $A$s are random. We make certain assumptions regarding the neural network model. These assumptions consider random variables $X$s and $A$s (their distributions and mutual dependencies) as well as they introduce spherical constraint on the model weights. We also introduce two other assumptions regarding redundancy of network parameters and their uniformity (details in the text below), both of them are justified by empirical evidence in the literature. The aim of this section is to obtain an approximator to the expectation $\mathbb{E}_A[Y]$ (note it is still a random variable) which, as will be seen in Section~\ref{subsec:LFSG}, is used in the definition of the loss function of neural network. Theorems~\ref{thm:redun} and~\ref{thm:unif} provide some guarantees regarding the quality of this approximation.

\paragraph{Input}
We assume each input $X_i$ is a normal random variable such that $X_i\sim N(0,1)$.

\paragraph{Paths}
We assume each path in Equation~\ref{eq:befrein} is equally likely to be active thus $A_{i,j}$'s will be modelled as Bernoulli random variables with the same probability of success $\rho$. By assuming the independence of $X$'s and $A's$ we get the following
\begin{equation}
\mathbb{E}_A[Y] = q\sum_{i=1}^{n_0}\sum_{j = 1}^\gamma X_{i}\rho\prod_{k = 1}^{H}w_{i,j}^{(k)}.
\label{eq:befrein2}
\end{equation}
We furthermore decouple~\cite{opac-b1095246} the paths by assuming their mutual independence. \textcolor{red}{We might wanna write more.}

\paragraph{Redundancy in network parametrization}
Let $\mathcal{W} = \{w_1,w_2,\dots,w_{\Lambda}\}$ be the set of all weights of the network. Let $\mathcal{A}$ denote the set of all $H$-length configuration of weights chosen from $\mathcal{W}$ (order of weights in a configuration does matter). Note that the size of $\mathcal{A}$ is therefore $N^H$. Also let $\mathcal{B}$ be a set such that each element correspond to the single configuration of weights from Equation~\ref{eq:befrein2}, thus $\mathcal{B} = \{(w_{1,1}^1,w_{1,1}^2,\dots,w_{1,1}^H),(w_{1,2}^1,w_{1,2}^2,\dots,w_{1,2}^H),\dots,\\(w_{n_0,\gamma}^1,w_{n_0,\gamma}^2,\dots,w_{n_0,\gamma}^H)\}$, where every single weight comes from set $\mathcal{W}$. Note that in general there exist elements in $\mathcal{A}$ that will never appear in $\mathcal{B}$ (unless we allow repetition of weights in $\mathcal{W}$). Thus Equation~\ref{eq:befrein2} can be equivalently written as 
\begin{equation}
Y_{\Lambda} \!:=\! \mathbb{E}_A[Y] \!=\! q\!\!\!\!\sum_{i_1,i_2,\dots,i_H=1}^{N}\!\!\!\!\!\!\!\sum_{j = 1}^{r_{i_1\!,i_2,\dots,i_H}}\!\!\!\!\!X_{i_1,i_2,\dots,i_H}^{(j)}\rho\!\prod_{k = 1}^{H}\!\!w_{i_k}.
\label{eq:befapprox}
\end{equation}
We will now explain the notation. It is overcomplicated for purpose, as this notation will be useful later on. $r_{i_1,i_2,\dots,i_H}$ denotes whether the configuration $(w_{i_1},w_{i_2},\dots,w_{i_H})$ appeared in Equation~\ref{eq:befrein2} or not, thus $r_{i_1,i_2,\dots,i_H} \in \{0\cup{1}\}$, and $\{X_{i_1,i_2,\dots,i_H}^{(j)}\}_{j=1}^{r_{i_1,i_2,\dots,i_H}}$ denote a set of random variables corresponding to the same weight configuration (since $r_{i_1,i_2,\dots,i_H} \in \{0\cup{1}\}$ this set has at most one element). Also $r_{i_1,i_2,\dots,i_H} = 0$ implies that summand $X_{i_1,i_2,\dots,i_H}^{(j)}\rho\prod_{k = 1}^{H}w_{i_k}$ is zeroed out). Note that $\sum_{j = 1}^{r_{i_1\!,i_2,\dots,i_H}}X_{i_1,i_2,\dots,i_H}^{(j)}$ could be replaced by $r_{i_1\!,i_2,\dots,i_H}X_{i_1,i_2,\dots,i_H}$ since $r_{i_1,i_2,\dots,i_H}$, but we choose this notation on purpose as it will be helpful later on. Furthermore, the following condition has to be satisfied: $\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}r_{i_1,i_2,\dots,i_H} = \Psi$. In the notation $Y_{\Lambda}$, index $\Lambda$ refers to the number of unique weights of a network (this notation will also be helpful later).

@@

\paragraph{Uniformity}
Consider network $\mathcal{M}$ to be a $(s,\epsilon)$-reduction image of $\mathcal{N}$ for some $s \leq \Lambda$ and $\epsilon \in [0,1]$. The output $Y_s$ of the image network can in general be expressed as
\[Y_s = q\sum_{i_1,\dots,i_H=1}^{s}\sum_{j=1}^{t_{i_1,\dots,i_H}}X_{i_1,\dots,i_H}^{(j)}\rho\prod_{k = 1}^{H}w_{i_k},
\]
where $t_{i_1,\dots,i_H} \in \{\mathbb{Z}^{+}\cup{0}\}$ is the number of times each configuration $(w_{i_1},w_{i_2},\dots,w_{i_H})$ repeats in Equation~\ref{eq:befapprox} and $\sum_{i_1,\dots,i_H=1}^{s}t_{i_1,\dots,i_H} = \Psi$. We assume that unique weights are close to being evenly distributed on the graph of connections of network $\mathcal{M}$. We call this assumption a \textit{uniformity assumption} (note it is analogous to the maximum entropy assumption). This assumption is in general consistent with the approach in~\cite{NIPS2013_5025}. In particular, this assumption implies that for all $(i_1,i_2,\dots,i_H):i_1,i_2,\dots,i_H \in \{1,2,\dots,s\}$ there exists a positive constant $c \geq 1$ such that the following holds
\begin{equation}
\frac{1}{c}\cdot\frac{\Psi}{s^H} \leq t_{i_1,i_2,\dots,i_H} \leq c\cdot\frac{\Psi}{s^H}.
\label{eq:uniform}
\end{equation}
The factor $\sqrt{\frac{\Psi}{s^H}}$ comes from the fact that for the network where every weight is uniformly distributed on the graph of connections (thus with high probability every node is adjacent to an edge with any of the unique weights) it holds that $\hat{r}_{i_1,i_2,\dots,i_H} = \sqrt{\frac{\Psi}{s^H}}$. Note that this condition can be sattified with small $c$ (close to $1$) if $s$ is sufficiently small.

For simplicity assume $\frac{\Psi}{s^H} \in \mathbb{Z}^{+}$ and $\sqrt[H]{\Psi} \in \mathbb{Z}^{+}$. Consider therefore an expression as follows
\begin{equation}
\hat{Y}_s = q\sum_{i_1,\dots,i_H=1}^{s}\sum_{j=1}^{\frac{\Psi}{s^H}}X_{i_1,\dots,i_H}^{(j)}\rho\prod_{k = 1}^{H}w_{i_k},
\label{eq:approx}
\end{equation}
which corresponds to a network for which the lower-bound and upper-bound in Equation~\ref{eq:uniform} match. Note that one can combine both summations in Equation~\ref{eq:approx} and re-index this equation to obtain
\begin{equation}
\hat{Y}_s = q\sum_{i_1,\dots,i_H=1}^{\Lambda}X_{i_1,\dots,i_H}\rho\prod_{k = 1}^{H}w_{i_k}.
\label{eq:approxfinal}
\end{equation}
The following theorem (Theorem~\ref{thm:unif}) captures the connection between $\hat{Y}_s$ and $Y_{s}$.

\begin{theorem}
Under the uniformity assumption of Equation~\ref{eq:uniform}, random variable $\hat{Y}_s$ in Equation~\ref{eq:approx} and random variable $Y_s$ in Equation~\ref{eq:befapprox} sattisy the following
\[corr(\hat{Y}_s,Y_s) \geq \frac{1}{c^2}
\]
\label{thm:unif}
\end{theorem}
We will refer to $\hat{Y}_s$ as an $(s,\epsilon,\delta)$-\textit{approximator} of $Y_{\Lambda}$, where the quality of this approximation is captured in Theorems~\ref{thm:redun} and~\ref{thm:unif}. Intuitively, for large networks (our analysis in Section~\ref{sec:theory} considers $\Lambda \rightarrow \infty$) one would expect $s$ to be small enough to simultaneously guarantee sufficiently small (close to $1$) $c$ and preserve good accuracy (small $\epsilon$). \textcolor{red}{That is because large networks have significantly more modelling power thus small $s$ is a natural form of controlling the overfitting. Besides then the data is mapped to a higher dimensional space.}

\paragraph{Spherical constraint}
We finally make a benign assumption that the weights sattisfy the spherical condition 
\begin{equation}
\frac{1}{\Lambda}\sum_{i=1}^{\Lambda}w_i^2 = \mathcal{C},
\label{eq:befspherical}
\end{equation}
where $\mathcal{C}$ is some positive constant.

In the next we will consider two frequently used loss functions, absolute loss and hinge loss, where we approximate $Y_{\Lambda}$ with $\hat{Y}_s$.

@@

where $Y_t$ is a random variable corresponding the true data labeling that takes values $-S$ or $S$ in case of the absolute loss and $-1$ or $1$ in case of the hinge loss, where $S = \sup_{\bf{w}}{\hat{Y}_s}$. Also note that in case of the hinge loss $\max$ operator can be modelled as Bernoulli random variable, that we will refer to as $M$, with success ($M = 1$) probability $\rho^{'} = \frac{1}{\rho\sqrt{\mathcal{C}^H}}$. We assume $M$ is independent of $\hat{Y}_s$. Therefore we obtain that

@@

  $\!\!\!\!\!\!\mathbb{E}_{M}[M(1 - \hat{Y}_s)]$ $\:\:\:\:$if$\:\:\:\:$ $Y_t = 1$ \\
  $\!\mathbb{E}_{M}[M(1 + \hat{Y}_s)]$ $\:\:\:\:$if$\:\:\:\:$ $Y_t = -1$ \\

@@

  $\!\mathbb{E}_{M}[M(S - \hat{Y}_s)]$ $\:\:\:\:$if$\:\:\:\:$ $Y_t  > 0$ \\
  $\!\mathbb{E}_{M}[M(S + \hat{Y}_s)]$ $\:\:\:\:$if$\:\:\:\:$ $Y_t < 0$ \\

@@

where in case of the absolute loss $\rho^{'} = 1$ and in case of the hinge loss $S = 1$. Furthermore, since $X$'s are Gaussian random variables, then so are $-X$'s thus we can further generalize that

@@

\mathcal{L}_{\Lambda,H}({\bm w}) \!\!\!\!\!&=&\!\!\!\!\! \mathbb{E}_{M}[M(S + \hat{Y}_s)]\\
&=& \!\!\!\!\!S\rho^{'} \!+\! \rho^{'}\hat{Y}_s\\
&=& \!\!\!\!\!S\rho^{'} \!+\! q\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}\!\!\!\!\!\!\!X_{i_1,i_2,\dots,i_H}\rho\rho^{'}\prod_{k = 1}^{H}w_{i_k}.
